### 2011-01-26 paper/platformDetails.tex
added robot_close to platform details
edited platform details

% Describe how you implemented your system and how you structured it. 
% This should give an overview of the system, not a detailed 
% documentation of the code. The documentation of the code is part of 
% the code you hand in. You might want to comment on high-level design 
% decisions that you made. Also explain how you obtained your
% data and any pre-processing you did to it.
\acmFig{quadratot.jpg}{1}{The robot}
\acmFig{topdown.png}{1}{A figure of the robot from a top-down perspective,
with motors labeled}

@@

A Wii remote tracks the location of the robot, providing feedback
about distance traveled, through an infrared LED mounted on top of 
the robot. A server is run on the robot and continuously tracks its
position using the CWiid library\cite{cwiid} to interface with the remote
via bluetooth. A client then connects via a socket to the tracking
server and requests position updates periodically. If the robot moves 
beyond the viewable range of the Wii remote, the system pauses and
directs the user to move the robot back within the viewable range 
before running again.

>>>>

% Describe how you implemented your system and how you structured it. 
% This should give an overview of the system, not a detailed 
% documentation of the code. The documentation of the code is part of 
% the code you hand in. You might want to comment on high-level design 
% decisions that you made. Also explain how you obtained your
% data and any pre-processing you did to it.
\acmFig{robot_close.jpg}{1}{The robot}
\acmFig{topdown.png}{1}{A figure of the robot from a top-down perspective,
with motors labeled}

@@

A Nintendo Wii remote tracks the location of the robot, providing feedback
about distance traveled, in pixels, through an infrared LED mounted on top of 
the robot. A server is run on the robot and continuously tracks its
position using the CWiid library\cite{cwiid} to interface with the remote
via bluetooth. A client then connects via a socket to the tracking
server and requests position updates periodically. If the robot walks 
beyond the viewable range of the Wii remote, a prompt informed the
user. The only human intervention required during the
experiment was to move the robot back inside the viewable area and resume
the run, and to handle any mechnanical failures that arose. This did not
interrupt the learning process or result in the loss of data.
